APPM report - Draft

### 2022-09-15 paper_version/main.tex
test
Copy-paste from master thesis. The main skeleton is done.

\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}

@@

\chapter{Introduction}

\end{document}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}

\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
\newcommand{\todobox}[1]{
    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
        #1
    \end{tcolorbox}
}

@@

\todobox{
    \begin{itemize}
        \item For the time being, the contents are just clipped from master thesis. They could be very chaotic.
        \item The figures are not added yet.
        \item For sure some parts need rewriting.
    \end{itemize}
}

\section*{Abstract}
A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose size indicates to what extent electric charges can deviate from the neutral case: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral. Plasma models have rather different properties in these two regimes due to the singular perturbation arising from the $\lambda_D\to 0$ limit.
Since both regimes may coexist in some plasma phenomena, it is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$. More precisely, they should be \emph{asymptotic-preserving} (AP), in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.

An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We start from their dimensionless model and extend the scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. This scheme turns out to be AP for $\lambda_D\to 0$ both in terms of structure and empirically in numerical test. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modeled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.

\section{Introduction}
Under moderate assumptions, plasmas, which are mixed gases of charged particles, can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields. In this work, we discuss and implement this so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero. The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations. To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain. In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem. Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain. Now comes the concept of \emph{asymptotic-preserving}(AP) scheme. We turn to the celebrated commuting diagram Fig. \ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.

The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system. The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for the Maxwell equations. The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD. The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair. These would be made clear in the corresponding sections.

\todo{add previous work on AP schemes, FIT, plasma simulation}.

The content of this paper is organized as follows. In Section 2 we introduce the full Maxwell-Euler model for plasmas, followed by the rescaling procedure which is crucial to define the rescaled Debye length $\lambda$ and to identify its limiting behavior. In the meantime, it is essential to discuss what boundary conditions are appropriate for this singular perturbation problem. Section 3 is then dedicated to a brief introduction about \cite{degond_2012} based on which our work is extended. In Section 4, we first discuss our FVM-FIT framework in details, especially how the unknowns are assigned on the staggered meshes and the boundary treatment in 3D case. Afterwards, the full discretization scheme is presented. Special care shall be taken to the treatment of boundary conditions and insulator part of the domain as $\lambda \rightarrow 0$, which is crucial to make the scheme AP. A numerical experiment for a 3D cylindrical domain is presented in Section 5 where we want to demonstrate the capability of our scheme in dealing with both non-neutral and quasi-neutral regimes of plasmas.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \node (nw) {\Large $P^\lambda_h$};
    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
    \node (sw) [below=of nw]{\Large $P^0_h$};
    \node (se) [right=3cm of sw]{\Large $P^0$};
    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
    \draw[->] (nw.east)  --  (ne.west) ;
    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
    \draw[->] (nw.south) -- node {} (sw.north);
    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
    \end{tikzpicture}
    \caption{Commuting diagram of AP schemes}
    \label{fig:commuting_diagram_ap}
\end{figure}

\section{The Maxwell-Euler System and its Rescalling}
\subsection{Full plasma fluid model}
The Maxwell system is described by Maxwell's equations whose expression in SI units read
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous mediums in vacuum. The quantities are thus related by the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.

In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}. Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination. The generic expressions read
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we would only consider ion-electron collision in this work. Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$. For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
\begin{equation*}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation*}

\subsection{Rescaled Maxwell-Euler system}
The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters. In particular, the quasi-neutrality approximation is clarified. The rescaling procedure mostly sticks to that of \cite{degond_2017}.

First, typical values for each quantity, as well as the characteristic length and time scale are specified. Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
\end{align*}
\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value. By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

Following the assumption in \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale with the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$. To study the quasi-neutral regime, the dimensionless Debye length $\lambda$ is an asymptotic parameter ranging in $[0,1]$. It is assumed that $\alpha$ has the same magnitude as $\lambda$, and $\eta$ and $\beta$ are of order one.

Special treatment is needed for the collision term. One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}. Therefore, for the sake of simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.

In summary, we make the following choices
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
\end{equation}

Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$. The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$.

\subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$. When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.

Such behavior is clearly explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}). By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap. 2]{remi_2014}}, the Maxwell system becomes 
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
One can notice that the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}). Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at the initial time.

The vanishing time derivative of $\mathbf{E}$-field is an indicator of the singular perturbation nature of the quasi-neutral model. To be specific, in the non-neutral model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}). To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}). Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the reformulated Maxwell's equations
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_reform}\\
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:maxwell_ampere_reform}\\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_reform}\\
    \lambda^2\nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_reform}
\end{align}
where
\begin{equation*}
    a = \sum_*\varepsilon_*^{-2}q_*^2n_*, \ \ \ \mathbf{b} = \sum_* \epsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2}p_*\mathbb{I}).
\end{equation*}
It is easy to check that (\ref{equ:maxwell_faraday_reform}) to (\ref{equ:maxwell_ampere_reform}) is equivalent to (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:maxwell_gauss_D_rescaled}) as soon as (\ref{equ:maxwell_ampere_rescaled}) is satisfied at the initial time. The equation (\ref{equ:maxwell_ampere_reform}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$. One of the key aims of designing an AP scheme is to reproduce this shift at the discrete level.

\subsection{Boundary conditions}
On yielding the rescaled system (?) - (?), we would like to discuss about the boundary conditions here. One cannot directly impose any BC suitable for the non-limit model since it could possibly be ill-posed for the limiting model. In our case, we dealing with the shifting between the full Maxwell equations and the eddy-current model.

Since the scheme is supposed to work for both regimes, the BCs ought to be uniformly well-posed. An example is given to convey the idea. Let's look at the continuous non-neutral Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled})
\begin{equation*}
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = - \mathbf{J},
\end{equation*}
which loses its hyperbolic character and becomes a constraint when $\lambda \rightarrow 0$. Now consider two boundary conditions
\begin{itemize}
    \item[-]  $\mathbf{E}\cdot\mathbf{n} = 0$ on $\partial\Omega$;
    \item[-] $\nabla \times \mathbf{B} \cdot\mathbf{n} = \mathbf{J}\cdot\mathbf{n}$ on $\partial\Omega$. 
\end{itemize}
They are equivalent when $\lambda$ is non-zero provided $\mathbf{E}\cdot\mathbf{n}|_{\partial\Omega}$ is zero at the initial time. However, setting $\lambda = 0$ destroys the equivalence. The second BC no longer implies the first one and becomes redundant since the quasi-neutral Amp\`{e}re's law already enforces such condition, which ruins the well-posedness of the quasi-neutral problem. Hence the first BC is the one that is supposed to be employed.

From the viewpoint of the discrete model, the continuous equations are discretized into a set of algebraic equations according to the scheme, and they are assembled into a linear system that needs to be solved at each time step. The redundancy of the second BC at limiting case results in the singularity of the linear system since the BC can be derived by linear operations from the algebraic form of the PDEs.

\todo{Give a sketch of an abstract domain, and assign BCs to each boundary for both Euler and Maxwell.}

\section{Previous Work: 1D Discretization}
In this section we briefly discuss the underlying work \cite{degond_2012} on which our work is built. Meanwhile, this section also serves as a preliminary case study such that readers can better understand the 3D scheme that we present. 
\subsection{1D plasma model}
The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig. \ref{fig:1d-frame} for the definition of reference frame). Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The collision between particles is omitted for the time being. 
\begin{figure}
    \centering
    \includegraphics[scale=0.2]{1d_frame.png}
    \caption{Projection of the 3D model onto $z$-axis. Let us consider a Cartesian mesh doublet. The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis. Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
    \label{fig:1d-frame}
\end{figure}

Take all the traverse derivatives $\partial_x, \partial_y$ and $u_y, E_y, B_x, B_z$ to be zero, we get the one-fluid Euler-Maxwell system in 1D:
\begin{align*}
    \partial_t n + \partial_z(nu_z) &= 0, \\
    \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
    \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
    \lambda^2 \partial_t E_z &= nu_z, \\
    \lambda^2 \partial_z E_z &= 1 - n,
\end{align*}
as well as the quasi-neutral limit by taking $\lambda \rightarrow 0$:
\begin{align*}
    n &= 1\\
    \varepsilon^2 \partial_t(u_x) &= - E_x, \\
    E_z + u_xB_y &= 0, \\
    u_z &= 0 \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \partial_z B_y &= nu_x
\end{align*}
\subsection{Finite difference on staggered grid}
\todo{Add illustration about 1D FDTD}
\subsection{Semi-implicit AP time-stepping}
Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
\begin{align}
    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \label{equ:1f1d-n}\\
    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nux}\\
    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nuz}\\ 
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \label{equ:1f1d-By}\\
    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \label{equ:1f1d-Ex}\\
    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, \label{equ:1f1d-Ez}
\end{align}
where 
\begin{equation*}
    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
\end{equation*}
is the consequence of interpolation of electromagnetic field, 
and the fluxes read
\begin{align*}
    f^{m+1/2}_{n,k+1/2} & = \frac{1}{2}[\textcolor{blue}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
    f^{m}_{u_x,k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
    f^{m}_{u_z,k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})]. \\
\end{align*}

\section{Discretization in 3D}
\subsection{Primal-dual staggered mesh}
A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws. The spatial domain is discretized by two meshes that interlace with each other. They are called \emph{primal} mesh $\mathcal{M}$ and \emph{dual} mesh $\Tilde{\mathcal{M}}$. The essential duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}. We demonstrate such interlacing character by an example in Fig. \ref{fig:illustration_primal_dual}, where the primal mesh is composed of triangular prisms and the dual mesh is composed of hexagon prisms. The dual mesh can be generated as the Voronoi decomposition of the primal mesh \citep{fuchs_2021}. Compared to the constraint of FDTD to Cartesian meshes, FIT is compatible with a wide range of mesh types. An example of primal and dual meshes is given in Fig. \ref{fig:primal_dual_meshes}.

To clarify the terminology, the \emph{vertices, edges, faces} and \emph{volumes} (denoted by $P,L,A$ and $V$ respectively) make up a mesh. Also, they are uniformly termed \emph{facets} with zero, one, two and three dimensions.
